### 2023-11-29 chapters/conclusion.tex
Minor edits

\textbf{In \cref{chp:introduction,chp:technical-background}} we introduced automated medical coding and stroke recognition as motivational cases. 
We used these cases to exemplify the importance of out-of-distribution detection, and, by extension, representation learning. In the context of these cases, we discussed possible machine learning system designs for decision-support and considered potential sources of uncertainty and ideal model behavior. 
As such, the cases have formed a reference point for the thesis as a whole with contributions within out-of-distribution detection as well as representation learning connecting to these applications. 
As \cref{chp:main-contributions} already details the contributions made by this thesis, we will not further discuss these in this conclusion.

@@

\vspace{1em}
\textbf{In \cref{chp:paper-hierarchical}} we showed how hierarchical variational autoencoders can fail at likelihood-based OOD detection due to an overemphasis on low-level features that generalize between different data distributions. By exploiting that VAEs tend to learn more abstract features at latent variables high in the hierarchy, we were able to define a likelihood-ratio score for OOD detection that focused more on features unlikely to be shared between datasets. 
% - VAEs can learn useful representations, but it can be hard to impose the appropriate constraints that enable this.
% - VAEs can learn representations that are useful for OOD detection, but good performance might require selecting an appropriate subset of feature dimensions to use for discriminating.
This work also highlights that overlap between distributions of high-dimensional data can severely impede OOD detection. Our work shows that a promising direction of future research is into how select which dimensions are the most discriminatory.

@@

\vspace{1em}
\textbf{In \cref{chp:paper-brief}} we provided an overview of unsupervised neural speech representation learning. Such approaches have recently matched supervised methods on many tasks and represent a significant advance in low-resource settings, such as speech recognition for minority languages. 
We found that for the purpose of learning good representations in an unsupervised manner, self-supervised learning seems to have better inductive biases, or at least pose a more forgiving learning problem, than do VAEs. As discussed in the paper and in \cref{sec_discussion:representation-learning-with-vaes}, this likely relates more to inductive biases imposed by implicit constraints in the optimization problem and architecture than to the underlying formalism. 
For instance, in discussion about the weaknesses of VAE-based approaches (\cref{sec_discussion:representation-learning-with-vaes}) we concluded that their challenges could not be directly attributed to the maximum marginal likelihood objective. Indeed, the masked pre-training objective widely used for successful self"=supervised methods also corresponds to a maximum marginal likelihood objective \parencite{moreno-munoz_masked_2023}.

@@

In \cref{sec: discussion-stroke-recognition-uncertainty}, we discussed how calibrating the predictive uncertainty of the stroke model is likely to be necessary to enable sustained use of such a model in practice. In \cref{fig_discussion:retrospective-paper-f1-performance-vs-predicted-probability}, we noted that, as expected, model performance measured by F1-score increased with increasing model certainty which underlines the likely usefulness of uncertainty estimates in helping to match practitioner expectations of such a model. Nonetheless, basic metrics of model performance are still obstacles for its practical usefulness. Specifically, the rarity of stroke cases lead to a false positive rate and precision that are likely to induce alarm fatigue among its users. Similar effects are likely to have influenced the practical impact of a similar system for cardiac arrest detection which showed significant improvements retrospectively \parencite{cite14} which, although matched by the model in a prospective study, did not ultimately result in improved call-taker performance \parencite{cite15}.

>>>>

\textbf{In \cref{chp:introduction}} we introduced automated medical coding and stroke recognition as motivational cases. 
We used these cases to exemplify the importance of out-of-distribution detection, and, by extension, representation learning. In the context of these cases, we discussed possible machine learning system designs for decision-support and considered potential sources of uncertainty and ideal model behavior. 
As such, the cases have formed a reference point for the thesis as a whole with contributions within out-of-distribution detection as well as representation learning connecting to these applications. 
As \textbf{\cref{chp:main-contributions}} already details the contributions made by this thesis, we will not reiterate these in detail in this conclusion.

@@

\vspace{1em}
\textbf{In \cref{chp:paper-hierarchical}} we showed how hierarchical variational autoencoders can fail at likelihood-based OOD detection due to an overemphasis on low-level features that generalize between different data distributions. By exploiting that VAEs tend to learn more abstract features at latent variables high in the hierarchy, we were able to define a likelihood-ratio score for OOD detection that focused more on features unlikely to be shared between datasets. 
% - VAEs can learn useful representations, but it can be hard to impose the appropriate constraints that enable this.
% - VAEs can learn representations that are useful for OOD detection, but good performance might require selecting an appropriate subset of feature dimensions to use for discriminating.
This work also highlights that overlap between distributions of high-dimensional data can severely impede OOD detection. Our work shows that a promising direction of future research is into how to select which dimensions are the most discriminatory.

@@

\vspace{1em}
\textbf{In \cref{chp:paper-brief}} we provided an overview of unsupervised neural speech representation learning. Such approaches have recently matched supervised methods on many tasks and represent a significant advance in low-resource settings, such as speech recognition for minority languages. 
We found that for the purpose of learning good representations in an unsupervised manner, self-supervised learning seems to have better inductive biases, or at least pose a more forgiving learning problem, than do VAEs. As discussed in \cref{chp:paper-brief,sec_discussion:representation-learning-with-vaes}, this likely relates more to inductive biases imposed by implicit constraints in the optimization problem and architecture than to the underlying formalism. 
For instance, in discussion about the weaknesses of VAE-based approaches (\cref{sec_discussion:representation-learning-with-vaes}) we concluded that their challenges could not be directly attributed to the maximum marginal likelihood objective. Indeed, the masked pre-training objective widely used for successful self"=supervised methods also corresponds to a maximum marginal likelihood objective \parencite{moreno-munoz_masked_2023}. 
This also leaves hope ... \moretodo{hope to improve VAEs by certain measures.}

@@

In \cref{sec: discussion-stroke-recognition-uncertainty}, we discussed how calibrating the predictive uncertainty of the stroke model is likely to be necessary to enable sustained use of such a model in practice. In \cref{fig_discussion:retrospective-paper-f1-performance-vs-predicted-probability}, we noted that, as expected, model performance measured by F1-score increased with increasing model certainty which underlines the likely usefulness of uncertainty estimates in matching practitioner expectations of the predictive performance. 
Nonetheless, basic metrics of model performance might still be obstacles for its practical usefulness. Specifically, the rarity of stroke cases lead to a false positive rate and precision that are likely to induce alarm fatigue among its users. Similar effects are likely to have influenced the practical impact of a similar system for cardiac arrest detection which showed significant improvements retrospectively \parencite{cite14} which, although matched by the model in a prospective study, did not ultimately result in improved call-taker performance \parencite{cite15}.
